Certified Knowledge Compilation \\ with Application to Verified Model Counting

### 2023-05-23 doc/lean.tex
make minor edits to paper

\vspace{1em}\noindent
\textbf{Proof checking.} The goal of a CPOG proof is to construct a POG that is equivalent to the input CNF $\inputformula$. The POG being constructed, and the set of active clauses are stored in the checker state \texttt{st}. The checker begins by parsing the input formula, initializing the active clauses to $\theta \leftarrow \inputformula$, and initializing the POG $P$ to an empty one. It then processes every step of the CPOG proof, either modifying its state by adding/deleting clauses in $\theta$ and adding nodes to $P$, or throwing an exception if a step is incorrect. Afterwards, it carries out the \textsc{final conditions} check of \cref{subsection:semantics}. Throughout the process, we maintain invariants which ensure that $P$ is partitioned and that a successful final check entails the logical equivalence of $\inputformula$ and $\phi_\noder$, where $\noder$ is the final POG root (\cref{thm:lean:equiv}).

@@

invariants.extends_pogDefsForm : extendsOver st.inputCnf.vars ⊤ st.pogDefsForm
invariants.uep_pogDefsForm : uniqueExt st.inputCnf.vars st.allVars st.pogDefsForm
\end{lstlisting}
The next invariant guarantees that the set of solutions over the original variables is preserved:
\begin{lstlisting}
def equivalentOver (X : Set Var) (φ₁ φ₂ : PropForm Var) :=
  extendsOver X φ₁ φ₂ ∧ extendsOver X φ₂ φ₁

>>>>

\vspace{1em}\noindent
\textbf{Proof checking.} The goal of a CPOG proof is to construct a POG that is equivalent to the input CNF $\inputformula$. The POG being constructed, and the set of active clauses are stored in the checker state \texttt{st}. The checker begins by parsing the input formula, initializing the active clauses to $\theta \leftarrow \inputformula$, and initializing the POG $P$ to an empty one. It then processes every step of the CPOG proof, either modifying its state by adding/deleting clauses in $\theta$ and adding nodes to $P$, or throwing an exception if a step is incorrect. Afterwards, it carries out the \textsc{final conditions} check of \cref{subsection:semantics}. Throughout the process, we maintain invariants that ensure that $P$ is partitioned and that a successful final check entails the logical equivalence of $\inputformula$ and $\phi_\noder$, where $\noder$ is the final POG root (\cref{thm:lean:equiv}).

@@

invariants.extends_pogDefsForm : extendsOver st.inputCnf.vars ⊤ st.pogDefsForm
invariants.uep_pogDefsForm : uniqueExt st.inputCnf.vars st.allVars st.pogDefsForm
\end{lstlisting}
Note that in the definition of \lstinline{uniqueExt}, the arrows associate to the right,
so the definition says that the three assumptions imply the conclusion.
The next invariant guarantees that the set of solutions over the original variables is preserved:
\begin{lstlisting}
def equivalentOver (X : Set Var) (φ₁ φ₂ : PropForm Var) :=
  extendsOver X φ₁ φ₂ ∧ extendsOver X φ₂ φ₁
